%!TeX program = pdflatex
% Erik Fredner's Curriculum Vitae

\documentclass[12pt,letterpaper]{report}

\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) for accented characters as single glyph
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % regionalize hyphens, quote marks, etc automatically
\usepackage{microtype}% improve text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto}    % make nice tabbing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts
\usepackage{setspace} % custom line spacing
\usepackage[dvipsnames]{xcolor} % Load xcolor with extended color names

% what is your name?
\newcommand{\myname}{Erik Fredner}

% select default typefaces
\usepackage{ebgaramond} % document's serif typeface
\usepackage{helvet}    % document's sans serif typeface

% how far to tab for list items with left-aligned date: different fonts need different widths
\newcommand{\listtabwidth}{1.7cm}

% define font to use as document's title
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*, family=\sfdefault}{30} % increase sans serif headings tracking
\titleformat{\section}{\lsstyle\sffamily\small\bfseries\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{30pt plus 4pt minus 4pt}{8pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\lsstyle\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{16pt plus 4pt minus 4pt}{4pt plus 2pt minus 2pt}

% set page margins (assumes letter paper)
\geometry{body={6.5in, 9.0in},
    left=1.0in,
    top=1.0in}

% prevent paragraph indentation
\setlength\parindent{0em}

% set line spacing
\setstretch{0.9}

% define space between list items
\newcommand{\listitemspace}{0.25em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
                \setlength{\parskip}{0em}
                \setlength{\itemsep}{\listitemspace}
                \setlength{\parsep}{\listitemspace}}}
{\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

% print only the month and year when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
    colorlinks  = true,
    urlcolor    = Blue,
    citecolor   = black,
    linkcolor   = black,
    pdfauthor   = {\myname},
    pdfkeywords = {data science, English, digital humanities, literary studies, computational literary history},
    pdftitle    = {\myname: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\begin{document}
\raggedright{}

% display your name as the document title
\namefont{\myname}

% affiliation and contact info blocks
\vspace{1em}
\begin{minipage}[t]{0.700\textwidth}
	% current primary affiliation, left-aligned
	University of Richmond\\
	Department of English\\
	Visiting Assistant Professor of Data Science
\end{minipage}
\begin{minipage}[t]{0.295\textwidth}
	% contact info details, right-aligned
	\flushright{}
	\href{mailto:erik.fredner@richmond.edu}{erik.fredner@richmond.edu} \\
	\href{https://fredner.org}{https://fredner.org} \\
	\href{https://orcid.org/0000-0002-2993-4961}{ORCID}
\end{minipage}

\section*{Education}

\begin{tablist}
	\item[Ph.D.] \tab{}Stanford University, English, 2014--2021 \\
	Graduate Certificate in Digital Humanities
	\item[A.B.]  \tab{}Harvard University, English \textit{magna cum laude}, 2008--2012
	\item[] \tab{}Harvard Graduate School of Education, Undergraduate Teacher Education Program, 2011--2012
	\item[] \tab{}University of Oxford, St Peter's College, Visiting Student of English Language \& Literature, 2010--2011
\end{tablist}

\section*{Appointments}

\begin{tablist}
	\item[2024--]   \tab{}University of Richmond \\
	Department of English\\
	Visiting Assistant Professor of Data Science
	\item[2021--24] \tab{}University of Virginia \\
	College of Arts and Sciences\\
	Postdoctoral Research Associate \& Lecturer
\end{tablist}

\section*{Publications}

\subsection*{Journal Articles}

\begin{tablist}
	\item[2024] \tab{}Erik Fredner and J. D. Porter. \enquote{Counting on \textit{The Norton Anthology of American Literature}.} \textit{PMLA/Publications of the Modern Language Association of America}, 139(1): 50--65. \href{https://doi.org/10.1632/S0030812923001189}{doi:10.1632/S0030812923001189}
	\item[2022] \tab{}Erik Fredner. \enquote{A Meaning Apart from Its Indistinguishable Words.} \textit{Nathaniel Hawthorne Review}, 48(1): 82--98. \href{https://doi.org/10.5325/nathhawtrevi.48.1.0082}{doi:10.5325/nathhawtrevi.48.1.0082}
	\item[2021] \tab{}Erik Fredner. \enquote{Hamlin Garland's ‘Problem of Individual Life’.} \textit{Nineteenth-Century Literature}, 76(3): 354--383. \href{https://doi.org/10.1525/ncl.2021.76.3.354}{doi:10.1525/ncl.2021.76.3.354}
	\item[2017] \tab{}David McClure, Mark Algee-Hewitt, Steele Douris, Erik Fredner, and Hannah Walser. \enquote{Organizing Corpora at the Stanford Literary Lab: Balancing Simplicity and Flexibility in Metadata Management.} \textit{Proceedings of the Workshop on Challenges in the Management of Large Corpora}, 25--29. \href{https://ids-pub.bsz-bw.de/frontdoor/index/index/docId/6261}{doi:10.5281/zenodo.1137914}
\end{tablist}

\subsection*{Book Chapter}

\begin{tablist}
	\item[2018] \tab{}Mark Algee-Hewitt, Erik Fredner, and Hannah Walser. \enquote{The Novel as Data.} In \textit{The Cambridge Companion to the Novel}, ed. Eric Bulson, 189--216. Cambridge University Press. \href{https://doi.org/10.1017/9781316659694.013}{doi:10.1017/9781316659694.013}
\end{tablist}

\subsection*{Review}

\begin{tablist}
	\item[2020] \tab{}Erik Fredner. \enquote{\emph{Enumerations: Data and Literary Study} by Andrew Piper.} \textit{Studies in the Novel}, 52(2): 220--222. \href{https://doi.org/10.1353/sdn.2020.0026}{doi:10.1353/sdn.2020.0026}
\end{tablist}

\subsection*{Dissertation}

\begin{tablist}
	\item[2021] \tab{}\enquote{Averaging Americans: Literature, Statistics, and Inequality} (\href{https://purl.stanford.edu/rp802rv5947}{url})
\end{tablist}

\subsection*{Book in Progress}

\textit{Averaging Americans: Why US Literature Started Thinking Statistically}

\smallskip

A computational literary history arguing that the increasing centrality of statistical thinking differentiates US fiction published after the Civil War. 85,000 words.

\subsection*{Essays in Progress}

\enquote{Anthologies at Scale} (with J.D. Porter)

\smallskip

Preliminarily accepted for \textit{Cultures of Scale: Disciplines, Data, and Labor}, edited by Joshua Ortiz Baco, Jim Casey, Benjamin Charles Germain Lee, and Sarah H. Salter. \textit{Debates in Digital Humanities}, edited by Matthew K. Gold and Lauren F. Klein. University of Minnesota Press. 6,000 words.

\bigskip

\enquote{Moving the Capital of US Literature from Boston to New York in 11 Million Library of Congress Records}

\smallskip

Under review. Analyzes the changing geographies of US literature imprints using data from Library of Congress book records. 2,000 words.

\bigskip

\enquote{The Ends of Reading: Reading Statistics and the Overestimation of Literary Studies' Aim}

\smallskip

Under review. Analyzes US Census Bureau statistics about reading for pleasure in the United States from 1982 to 2022. 10,000 words.

\bigskip

\enquote{\emph{The MLA International Bibliography}'s English-Language Literary History, 1981-2023} (with Mark Algee-Hewitt)

\smallskip

First large-scale analysis of about 900,000 records from the \textit{MLAIB} describing research on literatures in English. 10,000 words.

\bigskip

\enquote{The Literary Canon on \emph{Jeopardy!}, 1984-2023}

\smallskip

Identifies roughly 70,000 questions asked on \emph{Jeopardy!} that reference literature. Then, uses the pricing of those questions to measure the rarity of the knowledge they test. 5,000 words.

\section*{Awards}

\begin{tablist}
	\item[2024] \tab{}College Fellows Development Grant, University of Virginia \\
	In support of research on the representation of literature on \textit{Jeopardy!}
	\item[2022] \tab{}College Fellows Development Grant, University of Virginia \\
	In support of research on \textit{The MLA International Bibliography}
	\item[2020--21] \tab{}Mellon Foundation Dissertation Fellowship, Stanford Humanities Center
	\item[2018--19] \tab{}CUNY-Stanford Exchange Fellow, The City College of the City University of New York
	\item[2017--18] \tab{}G.J. Pigott Scholar, Stanford University
	\item[2017] \tab{}Excellence in Teaching Award, Stanford University, Department of English
\end{tablist}

\section*{Teaching}

\emph{Select syllabi and code \href{https://fredner.org/teaching}{available online.}}

\medskip

\begin{tablist}
	\item[2025] \tab{}Data Science and Statistics 389: \enquote{Advanced Data Science,} University of Richmond
	\item[2024] \tab{}Data Science and Statistics 289: \enquote{Introduction to Data Science,} University of Richmond
	\item[2024] \tab{}\enquote{Text Classification with Large Language Models,} The Text Analysis Pedagogy Institute, ITHAKA
	\item[2021--24] \tab{}Empirical and Scientific Engagement 1520: \enquote{From Language to Data,} University of Virginia
	\item[2021--24] \tab{}Engaging Aesthetics 1510: \enquote{Punching Up: US Satire,} University of Virginia
	\item[2020] \tab{}Summer Research Program, Center for Spatial and Textual Analysis, Stanford University
	\item[2018--20] \tab{}English 184E: \enquote{Literary Text Mining,} Stanford University \\
	Instructor of record (2018): Ryan Heuser
	\item[2018--19] \tab{}World Humanities 101: \enquote{\enquote{What it is like to be alive,}} The City College of New York
	\item[2017--18] \tab{}English 396L: Pedagogy, Stanford University \\
	Instructor of record: Paula Moya
	\item[2017--18] \tab{}English 162W: \enquote{Average Americans:} Writing Intensive Seminar in English, Stanford University
	\item[2015--16] \tab{}English 161: \enquote{Narrative and Narrative Theory,} Stanford University \\
	Instructors of record: Paula Moya and J.D. Porter
	\item[2014--15] \tab{}English 100C: \enquote{Literary History III (1850-1950),} Stanford University \\
	Instructor of record: Franco Moretti
\end{tablist}


\section*{Presentations}

\begin{tablist}
	\item[2024] \tab{}\enquote{The Ends of Reading,} Faculty and Staff Symposium, University of Richmond
	\item[2024] \tab{}\enquote{\emph{The MLA International Bibliography}'s History of English-Language Literary Studies,} Alliance of Digital Humanities Organizations, George Mason University, Arlington, Virginia
	\item[2024] \tab{}\enquote{Anthologies as Databases,} Digital Americanists Panel, The American Literature Association, Chicago, Illinois
	\item[2024] \tab{}\enquote{The Ends of Reading: Reading Statistics and the Overestimation of Literary Studies' Aim,} "Reader Studies in the Digital Age" symposium, Price Lab for Digital Humanities at the University of Pennsylvania
	\item[2024] \tab{}\enquote{How Much is Literary Knowledge Worth on \emph{Jeopardy}?} Stanford Literary Lab
	\item[2024] \tab{}\enquote{How to Publish (Computational) Literary Studies Research,} Stanford University, Department of English
	\item[2024] \tab{}\enquote{Challenging Nineteenth-Century Data Legacies,} Mellon Sawyer Seminar, Stanford Center for Spatial and Textual Analysis
	\item[2024] \tab{}\enquote{Mining \emph{The MLA International Bibliography},} Stanford Literary Lab
	\item[2024] \tab{}\enquote{Mining \emph{The MLA International Bibliography},} Modern Language Association, Philadelphia, Pennsylvania
	\item[2024] \tab{}\enquote{Du Bois, Statistical Thinking, and Irony,} Modern Language Association, Philadelphia, Pennsylvania
	\item[2023] \tab{}\enquote{Implications of Large Language Models for Teaching and Research,} University of Virginia, Charlottesville, Virginia
	\item[2023] \tab{}\enquote{How Literary Canons Evolve: A Data-Driven Approach,} The College of William \& Mary
	\item[2023] \tab{}\enquote{\emph{Elden Ring} and Exegesis,} University of Virginia
	\item[2023] \tab{}\enquote{What Good is Distant Reading for Our Reading?} Duke University
	\item[2022] \tab{}\enquote{On Scholarly Podcasting,} Stanford Center for Spatial and Textual Analysis
	\item[2022] \tab{}\enquote{Counting on \emph{The Norton Anthology of American Literature},} DH Unbound, The Association for Computers and the Humanities
	\item[2021] \tab{}\enquote{Counting on Literature,} University of Virginia
	\item[2021] \tab{}\enquote{Length and Weight,} Universitatea Lucian Blaga, Sibiu, Romania
	\item[2021] \tab{}\enquote{Introduction to Computational Text Analysis in Python,} Center for Spatial and Textual Analysis
	\item[2021] \tab{}\enquote{New Histories of Quantitative and Computational Methods,} Modern Language Association, Toronto, Canada
	\item[2020] \tab{}\enquote{Citizenship at Scale,} C19 2020, University Park, Pennsylvania
	\item[2020] \tab{}\enquote{Antebellum and Postbellum,} Stanford Literary Lab
	\item[2020] \tab{}\enquote{Typicality in the US Novel,} Alliance of Digital Humanities Organizations, Ottawa, Canada
	\item[2020] \tab{}\enquote{Celebrities,} Stanford Literary Lab
	\item[2020] \tab{}\enquote{Introduction to Computational Text Analysis in Python,} Stanford Center for Spatial and Textual Analysis
	\item[2020] \tab{}\enquote{Presider: Models of Enlightenment Knowledge,} Modern Language Association, Seattle, Washington
	\item[2020] \tab{}\enquote{Modeling Hawthorne's Concept of the Nation,} Modern Language Association, Seattle, Washington
	\item[2019] \tab{}\enquote{Microgenres,} Alliance of Digital Humanities Organizations, Utrecht, Netherlands
	\item[2018] \tab{}\enquote{\emph{n} Types of Typicality,} Stanford Literary Lab
	\item[2018] \tab{}\enquote{Norton Anthologies: Database, Canon, Career,} Stanford Literary Lab
	\item[2018] \tab{}\enquote{The Statistical Imaginations of Hamlin Garland and Henry James,} Stanford University, Department of English
	\item[2018] \tab{}\enquote{Typicality,} Stanford Literary Lab
	\item[2017] \tab{}\enquote{Distant Reading with the \emph{Oxford English Dictionary},} Stanford Literary Lab
	\item[2017] \tab{}\enquote{Average, American: Reformism and Statistics in \emph{Jason Edwards},} Stanford Consortium on the Novel
	\item[2017] \tab{}\enquote{The Type of the Average,} Stanford Working Group on the Novel
	\item[2017] \tab{}\enquote{Microgenres,} Stanford Literary Lab
	\item[2017] \tab{}\enquote{Reading the Norton Anthologies,} Alliance of Digital Humanities Organizations, Montréal, Canada
	\item[2017] \tab{}\enquote{Security in \emph{Foreign Affairs},} Stanford Literary Lab
	\item[2017] \tab{}\enquote{Synchronic and Diachronic Suspense,} Stanford Literary Lab
	\item[2017] \tab{}\enquote{How Many Novels Have Been Published in English?,} Stanford Literary Lab
	\item[2016] \tab{}\enquote{Reading Norton Anthologies,} SyncDH, University of California, Santa Barbara
	\item[2016] \tab{}\enquote{Reading the Norton Anthologies: Databases, Canons, and Careers,} Stanford Literary Lab
	\item[2016] \tab{}\enquote{Standing Underneath: Melville, Confidence, Testimony,} Berkeley-Stanford Conference, University of California, Berkeley
	\item[2015] \tab{}\enquote{Fallible and Unreliable Narration in \emph{The Sound and The Fury},} Stanford University, Narrative and Narrative Theory
	\item[2015] \tab{}\enquote{Another Castle: The Stolen Princess Narrative in Literature and Video games,} Stanford University, Infinite Possibilities: The Speculative Fiction Working Group
	\item[2015] \tab{}\enquote{Virality,} Alliance of Digital Humanities Organizations, Sydney, Australia
	\item[2015] \tab{}\enquote{Suspense… Language, Narrative, Affect,} Alliance of Digital Humanities Organizations, Sydney, Australia
	\item[2015] \tab{}\enquote{Current Projects of the Literary Lab,} SyncDH, University of California, Santa Barbara
	\item[2015] \tab{}\enquote{Two Blocks Joined by a Corridor: Time in \emph{To The Lighthouse},} Stanford Literary History
	\item[2014] \tab{}\enquote{Inveigling \emph{Uncle Tom's Cabin} to Become a Ballet: cummings's \emph{Tom},} Berkeley-Stanford Conference, Stanford, California
	\item[2014] \tab{}\enquote{On the Stanford Literary Lab's Pamphlet Series,} Future of Publication Workshop, Stanford, California
\end{tablist}


\section*{Research Collaborations}

\begin{tablist}
	\item[2022--] \tab{}\enquote{Counting on Anthologies of African American Literature,} with J.D. Porter (University of Pennsylvania); Arthur Knight and Alexander Nwala (College of William \& Mary)
	\item[2021--] \tab{}\enquote{\emph{The MLA International Bibliography} as Literary History,} with Mark Algee-Hewitt (Stanford Literary Lab)
	\item[2018--] \tab{}\enquote{Typicality,} with Mark Algee-Hewitt (Stanford Literary Lab)
	\item[2017--] \tab{}\enquote{Microgenres,} with Mark Algee-Hewitt, Michaela Bronstein, Abigail Droge, Ryan Heuser, Alexander Manshel, Nichole Nomura, J.D. Porter, and Hannah Walser (Stanford Literary Lab)
	\item[2015--] \tab{}\enquote{Security,} with Mark Algee-Hewitt, Whitney McIntosh, and Stephen Stedman (Stanford Literary Lab)
	\item[2014--] \tab{}\enquote{Suspense,} with Mark Algee-Hewitt, Abigail Droge, Tasha Eccles, Morgan Day Frank, J.D. Porter, Andrew Shephard, and Hannah Walser (Stanford Literary Lab)
\end{tablist}

\section*{Public Humanities}

\subsection*{Roles}

\begin{tablist}
	\item[2019--21] \tab{}Data scientist, \enquote{The Stuff of Fame,} discourses of celebrity in the US, Stanford Literary Lab \& Smithsonian Institution
	\item[2019--21] \tab{}Editor, \href{https://novel.stanford.edu/csn-cafe}{\emph{Café}} podcast, Stanford Center for the Study of the Novel
	\item[2017--21] \tab{}Presenter, Data privacy and security workshops, Stanford University Department of English
	\item[2016--] \tab{}Contributor, \href{https://litlab.stanford.edu/techne/}{\emph{Techne}}, Stanford Literary Lab
	\item[2014--16] \tab{}Writer, \href{https://web.archive.org/web/20221003115514/https://killscreen.com/previously/author/erik-fredner/}{\emph{Kill Screen}} magazine, Kill Screen Media, Inc.
	\item[2014--16] \tab{}Writer, Ph.D. Journalist Project, Stanford Humanities Center
\end{tablist}

\subsection*{Articles}

\begin{tablist}
	\item[\emph{forthc.}] \tab{}\enquote{Read for Pleasure!,} Center for Humanities Communication
	\item[2020] \tab{}\href{https://web.archive.org/web/20220430165427/https://litlab.stanford.edu/typicality-in-the-u-s-novel/}{\enquote{Typicality in US Literature},} \emph{Techne}
	\item[2019] \tab{}\href{https://web.archive.org/web/20220430054802/https://litlab.stanford.edu/finding-needles-in-34-million-haystacks/}{\enquote{Finding needles in 34 million haystacks},} \emph{Techne}
	\item[2017] \tab{}\href{https://web.archive.org/web/20220323072937/https://litlab.stanford.edu/how-many-novels-have-been-published-in-english-an-attempt/}{\enquote{How many novels have been published in English? An Attempt,}} \emph{Techne}
	\item[2016] \tab{}\href{https://web.archive.org/web/20230328175329/https://killscreen.com/previously/articles/the-peculiar-future-of-videogame-history/}{\enquote{The peculiar future of video game history,}} \emph{Kill Screen}
	\item[2015] \tab{}\href{https://web.archive.org/web/20210810123746/https://news.stanford.edu/news/2015/february/boland-country-book-022615.html}{\enquote{Eavan Boland interrogates identity and nationhood in new collection,}} \emph{The Humanities at Stanford}
	\item[2015] \tab{}\href{https://web.archive.org/web/20210810125202/https://news.stanford.edu/news/2015/may/melville-scholar-boone-051115.html}{\enquote{Stanford literary scholar: White whales and the "Melville Effect,"}} \emph{The Humanities at Stanford}
	\item[2014] \tab{} \href{https://web.archive.org/web/20231028015401/https://killscreen.com/previously/articles/year-anti-games/}{\enquote{The year in anti-games,}}
	\emph{Kill Screen}
	\item[2014] \tab{}\href{https://web.archive.org/web/20220611230152/https://news.stanford.edu/pr/2014/pr-mandela-statue-parker-120314.html}{\enquote{Stanford scholar questions whether statues appropriate way to commemorate Mandela,}} \emph{The Humanities at Stanford}
\end{tablist}

\subsection*{Podcasts}

\begin{tablist}
	\item[2022] \tab{}\href{https://virginiaaudio.org/\#/symposia/}{\enquote{Matriculation: The Academic Transition to College,}} \emph{Symposia}, Brown Residential College at the University of Virginia
	\item[2021] \tab{}\href{https://web.archive.org/web/20220429010015/https://novel.stanford.edu/csn-cafe/2021/7/23/crime-narratives-with-andrea-goulet-michelle-robinson-and-hctor-hoyos-43021-je87a}{Andrea Goulet, Michelle Robinson, and Héctor Hoyos on crime narrative}, \emph{Café}, Stanford Center for the Study of the Novel
	\item[2021] \tab{}\href{https://web.archive.org/web/20220429093420/https://novel.stanford.edu/csn-cafe/2021/7/23/nicholas-paige-technologies-of-the-novel-2821}{Nicholas Paige on \emph{Technologies of the Novel}}, \emph{Café}, Stanford Center for the Study of the Novel
	\item[2021] \tab{}\href{https://web.archive.org/web/20220429093353/https://novel.stanford.edu/csn-cafe/2021/7/23/books-at-the-center-dorothy-hale-the-novel-and-the-new-ethics-11521}{Dorothy Hale, Nancy Ruttenburg, and Alex Woloch on \emph{The Novel and the New Ethics}}, \emph{Café}, Stanford Center for the Study of the Novel
	\item[2021] \tab{}\href{https://web.archive.org/web/20220429093326/https://novel.stanford.edu/csn-cafe/2021/7/23/sharon-marcus-on-her-ian-watt-lecture-103020}{Sharon Marcus on the 2020 Ian Watt Lecture}, \emph{Café}, Stanford Center for the Study of the Novel
	\item[2020] \tab{}\href{https://web.archive.org/web/20220429010109/https://novel.stanford.edu/csn-cafe/2021/7/23/wai-chee-dimock-john-plotz-and-colin-milburn-on-the-literature-of-planetary-futures-52319}{Wai Chee Dimock, John Plotz, and Colin Milburn on planetary futures}, \emph{Café}, Stanford Center for the Study of the Novel
	\item[2020] \tab{}\href{https://web.archive.org/web/20220429010041/https://novel.stanford.edu/csn-cafe/2021/7/23/ato-quayson-john-kerrigan-and-richard-halpern-on-postcolonial-tragedy-91519}{Ato Quayson, John Kerrigan, and Richard Halpern on postcolonial tragedy}, \emph{Café}, Stanford Center for the Study of the Novel
	\item[2020] \tab{}\href{https://web.archive.org/web/20220429093237/https://novel.stanford.edu/csn-cafe/2021/7/23/fashion-stories-emily-apter-rhonda-garelick-and-anne-higonnet-on-the-cultural-history-of-clothing-1920}{Emily Apter, Rhonda Garelick, and Anne Higonnet on fashion stories}, \emph{Café}, Stanford Center for the Study of the Novel
	\item[2020] \tab{}\href{https://web.archive.org/web/20220429093211/https://novel.stanford.edu/csn-cafe/2021/7/23/books-at-the-center-stephen-best-mario-tel-and-kris-cohen-on-none-like-us-101019}{Stephen Best, Mario Telò, and Kris Cohen on \emph{None Like Us}}, \emph{Café}, Stanford Center for the Study of the Novel
	\item[2019] \tab{}\href{https://web.archive.org/web/20220429093144/https://novel.stanford.edu/csn-cafe/2021/7/23/rita-felski-on-her-2019-ian-watt-lecture-5319}{Rita Felski on the 2019 Ian Watt Lecture}, \emph{Café}, Stanford Center for the Study of the Novel
\end{tablist}

\section*{Service}

\begin{tablist}
	\item[2024--] \tab{}Generative Artificial Intelligence Committee, University of Richmond, Department of English
	\item[2024--] \tab{}Reviewer, National Endowment for the Humanities—Office of Digital Humanities
	\item[2023--] \tab{}Invited Referee, European Research Council
	\item[2022--] \tab{}Reviewer, \textit{Digital Scholarship in the Humanities}
	\item[2020] \tab{}Consultant, Stanford University Department of English virtual instruction transition
	\item[2017--20] \tab{}Website manager, Stanford Literary Lab
	\item[2016--] \tab{}Reviewer, Alliance of Digital Humanities Organizations Conference
	\item[2015--19] \tab{}Liaison, Berkeley-Stanford English Graduate Student Councils
	\item[2015--18] \tab{}Examiner, American Literature Practice Qualifying Exams
	\item[2014--19] \tab{}Coordinator, Stanford Literary Lab
\end{tablist}

\subsection*{Conferences Organized}

\begin{tablist}
	\item[2017] \tab{}\enquote{Findings: Is computation changing the study of literature?} Stanford University
	\item[2016] \tab{}\enquote{Literature: A history of the word,} Stanford University
	\item[2015] \tab{}\enquote{Making and Breaking: The Berkeley-Stanford Conference,} University of California, Berkeley
	\item[2015] \tab{}\enquote{Micromégas: The Objects of the Digital Humanities,} Stanford University
\end{tablist}


\section*{Affiliations}

\begin{tablist}
	\item[2020--] \tab{}The Association for Computers and the Humanities
	\item[2019--] \tab{}C19: The Society of Nineteenth-Century Americanists
	\item[2014--] \tab{}Alliance of Digital Humanities Organizations
	\item[2014--] \tab{}Modern Language Association
\end{tablist}

\section*{Technical}

\begin{tablist}
	\item\tab{}HTML
	\item\tab{}Pandoc
	\item\tab{}Python
	\item\tab{}R
	\item\tab{}Quarto
	\item\tab{}Tableau
	\item\tab{}TEI
	\item\tab{}TeX
	\item\tab{}Tidyverse
	\item\tab{}XML
\end{tablist}

\section*{Languages}

\begin{tablist}
	\item\tab{}Spanish (intermediate)
	\item\tab{}French (reading)
\end{tablist}

% display today's date as Month Year after a vertical space below the end of the text
\vfill
\begin{center}
	Updated \today.
\end{center}
\end{document}